Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-03 doc/prelim/presentation/prelim_presentation.tex
removing reproducibility slide
reworked storage slide. added asymptotic relationships

%%---------------------------------------------------------------------------%%
\begin{frame}{Reproducibility}

  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{0.7}{ \input{gentile_example.pdftex_t} }
    \end{center}
    \caption{\textbf{Gentile's example illustrating how domain
        decomposition can create reproducibility issues in Monte
        Carlo.}}
    \label{fig:gentile_example}
  \end{figure}

  \begin{itemize}
  \item 2005 work by Gentile outlines reproducibility in parallel
    Monte Carlo
  \item Maintaining random number sequences
  \item Floating point addition does not commute
  \item Useful for benchmarking and unit testing
  \end{itemize}

@@

  \pause
  \begin{itemize}
  \item $m$ Krylov iterations require $(m+1)$ subspace vectors
  \item Storage requirement is $\big[(m+1) N\big]$ for $\ve{x} \in
    \mathbb{R}^{N \times N}$
  \end{itemize}

  \pause
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {If we need 10 Krylov iterations to converge...}
    \begin{itemize}
    \item 66 elements required for subspace vectors
    \item 72 total elements required for Jacobian and probability
      matrix
    \end{itemize}
  \end{beamerboxesrounded}

>>>>

@@

  \begin{itemize}
  \item CRS matrix with $q$ bands storage: $\big[(2q+1)N\big]$ for $\ve{x} \in
    \mathbb{R}^{N \times N}$ 
    \pause
  \item $m$ Krylov iterations require $(m+1)$ subspace vectors
  \item Subspace storage: $\big[(m+1) N\big]$ for $\ve{x} \in
    \mathbb{R}^{N \times N}$
  \end{itemize}

  \pause 
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {If we need 25 Krylov iterations to converge...}
    \begin{itemize}
    \item Break even scenario: $4q+1 = m$
    \item Jacobian and probability matrix with 6 bands or less is
      cheaper
    \end{itemize}
  \end{beamerboxesrounded}
